Study protocol

### 2021-03-22 Manuscript/Protocol.Rmd
reorganize comments

```{r one call, echo = TRUE, eval = FALSE}
# First create the Records/Session1/Query1 folder and put the manually downloaded files there if you have any. Otherwise the folders will be created automatically
Records <- perform_search_session(query = query, year_query = year_filter,
											 session_name = 'Session1', query_name = 'Query1',
											 journal = 'Session_journal.csv') %>% # perform searches and parse files; save and return the journal
	extract_source_file_paths() %>% # return the record file paths
	save_annotation_file(reorder_query = query, session_name = 'Session1') # read, join, reorder records and save them in the Annotations folder
```

>>>>

```{r one call, echo = TRUE, eval = FALSE}
# First create the Records/Session1/Query1 folder and put the manually
# downloaded files there if you have any. Otherwise the folders will be created
# automatically

# perform searches and parse files; save and return the journal
Records <- perform_search_session(query = query, year_query = year_filter,
											 session_name = 'Session1', query_name = 'Query1',
											 journal = 'Session_journal.csv') %>% 
	# return the record file paths
	extract_source_file_paths() %>%
	# read, join, reorder records and save them in the Sessions folder
	save_annotation_file(reorder_query = query, session_name = 'Session1') 
```
